\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\title{Recipe for the Thickest and Fluffiest Pancakes Ever}
\author{Allegra Bryant}
\date{September 3rd, 2019}

\begin{document}
\pagenumbering{roman}
\maketitle
\newpage
\section{Description of the Pancakes}
 This is the holy grail of pancake recipes if what you're looking for is a thick and fluffy pancake.  

\section{Ingredients for the Pancakes}
\begin{enumerate}
    \item 1.5 cups all-purpose flour
    \item 3.5 teaspoons baking powder
    \item 0.5 teaspoons salt
    \item 0.25 cups white sugar
    \item 1.25 cups milk
    \item 1 egg
    \item 3 tablespoons melted butter
\end{enumerate}

\section{How to make the Pancakes}
\begin{enumerate}
    \item Melt the butter in a microwave for 30 seconds, and then set aside.
    \item In a medium bowl, mix together flour, salt, sugar, and baking powder.
    \item Stir together the milk and egg.
    \item Create a well in the center of the flour mixture, pour in the milk and egg mixture, and pour in the melted butter.
    \item Using a wire whisk, stir everything together until just combined. It will be slightly thick and lumpy, but should be well incorporated. 
    \item Allow the batter to rest while heating a lightly oiled skillet (preferably cast iron) or griddle to medium high heat. 
    \item Pour or scoop the batter onto the griddle, using approximately 0.25 cup for each pancake. 
    \item Cook each side for 3-6 minutes, until lightly golden brown. 
\end{enumerate}
\end{document}
